\LARGE \bf TODO Name this thing

### 2012-02-09 papers/itsc_2012/root.tex
converted paper draft to ieee format

\documentclass[12pt]{article}

% TODO grab the ieee format

\title{Paper}
\author{Dustin Carlino, Mike Depinet, Piyush Khandelwal, Peter Stone}
\date{...}

\begin{document}
\maketitle

@@

@@

\section{Architecture}

@@

\section{Map Construction from OSM}

% briefly introduce OSM, advantages, etc

@@

\section{Simulation}

@@

\section{Experimental Results}

@@

\section{Notes}

possible background/links
%http://www.caliper.com/transmodeler/default.htm
%http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6082793
%https://www.google.com/search?sourceid=chrome&ie=UTF-8&q=Agent-Based+Traffic+Simulation+and+Traffic+Signal+Timing+Optimization+with+GPU

>>>>

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\title{\LARGE \bf
TODO Name this thing
}

% TODO which style do we use for authors? and do we list all 4 of us here?

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Huibert Kwakernaak$^{1}$ and Pradeep Misra$^{2}$% <-this % stops a space
\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak at papercept.net}}%
\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small p.misra at ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
Write this.
\end{abstract}

\section{INTRODUCTION}

@@

Write an intro.

@@

\section{ARCHITECTURE}

@@

\section{MAP CONSTRUCTION FROM OSM}

% TODO briefly introduce OSM, advantages, etc

@@

\section{SIMULATION}

@@

\section{EXPERIMENTAL RESULTS}

@@

\section{CONCLUSIONS}

Write me.

\addtolength{\textheight}{-12cm}  % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

\section*{APPENDIX}

Probably stuff about getting and using the code.

\section*{ACKNOWLEDGMENT}

Dr. Quinlan has certainly been helpful.

% Notes.

%possible background/links

%http://www.caliper.com/transmodeler/default.htm
%http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6082793
%https://www.google.com/search?sourceid=chrome&ie=UTF-8&q=Agent-Based+Traffic+Simulation+and+Traffic+Signal+Timing+Optimization+with+GPU

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\end{thebibliography}
